Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-14 manuscript/manuscript.tex
decapitalize all instances of Notebook and fix notebook number typo (addresses #171)

The estimation of an MSM requires the dynamics between microstates to be Markovian.
However, in case of a poor dimension reduction and/or discretization or short trajectories,
we cannot anticipate this to be the case.
We illustrate this point in Notebook~07.

@@

An HMM estimation always yields a model with a small number of (hidden) states
where each state is considered to be metastable and,
thus, the number of hidden states is a new hyper-parameter which needs to be chosen carefully (see Notebook~07).
As the HMMs---like MSMs---approximate the full phase-space dynamics,
we can similarly compute the metastable kinetics, apply TPT, visualize the network, and obtain physical observables.

@@

Here, we utilize the VAMP-2 score, which maximizes the kinetic variance contained in the features~\cite{kinetic-maps}.
We should always evaluate the score in a cross-validated manner to ensure that we neither include too few features (under-fitting) or too many features (over-fitting)~\cite{gmrq,vamp-preprint}.
To choose among three different molecular features reflecting protein structure,
we compute the (cross-validated) VAMP-2 score (Notebook 00).
Although we cannot MSM optimize lag times with a variational score\cite{husic2017note}, such as VAMP-2,
it is important to ensure that properties that we optimize are robust as a function of lag time. 
Consequently, we compute the VAMP-2 score at several lag times (Notebook 00). 
We find that the relative rankings of the different molecular features are highly robust as a function of lag time. 
We show one example of this ranking and the absolute VAMP-2 scores for lag time~$0.5$~ns in Fig.~\ref{fig:io-to-tica}b. 
We find that backbone torsions contain more kinetic variance than the backbone heavy atom positions or the distances between them (Fig.~\ref{fig:io-to-tica}b).
This suggests that backbone torsions are the best of the options evaluated for MSM construction.

@@

Additional technical challenges for large systems include high demands on memory and computation time;
we explain how to deal with those in the tutorials (Notebook 00 and 02).

>>>>

The estimation of an MSM requires the dynamics between microstates to be Markovian.
However, in case of a poor dimension reduction and/or discretization or short trajectories,
we cannot anticipate this to be the case.
We illustrate this point in notebook~07.

@@

An HMM estimation always yields a model with a small number of (hidden) states
where each state is considered to be metastable and,
thus, the number of hidden states is a new hyper-parameter which needs to be chosen carefully (see notebook~07).
As the HMMs---like MSMs---approximate the full phase-space dynamics,
we can similarly compute the metastable kinetics, apply TPT, visualize the network, and obtain physical observables.

@@

Here, we utilize the VAMP-2 score, which maximizes the kinetic variance contained in the features~\cite{kinetic-maps}.
We should always evaluate the score in a cross-validated manner to ensure that we neither include too few features (under-fitting) or too many features (over-fitting)~\cite{gmrq,vamp-preprint}.
To choose among three different molecular features reflecting protein structure,
we compute the (cross-validated) VAMP-2 score (notebook 00).
Although we cannot MSM optimize lag times with a variational score\cite{husic2017note}, such as VAMP-2,
it is important to ensure that properties that we optimize are robust as a function of lag time. 
Consequently, we compute the VAMP-2 score at several lag times (notebook 00). 
We find that the relative rankings of the different molecular features are highly robust as a function of lag time. 
We show one example of this ranking and the absolute VAMP-2 scores for lag time~$0.5$~ns in Fig.~\ref{fig:io-to-tica}b. 
We find that backbone torsions contain more kinetic variance than the backbone heavy atom positions or the distances between them (Fig.~\ref{fig:io-to-tica}b).
This suggests that backbone torsions are the best of the options evaluated for MSM construction.

@@

Additional technical challenges for large systems include high demands on memory and computation time;
we explain how to deal with those in the tutorials (notebooks~00 and~01).
